Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-06 paper.tex

\subsection{Testbed Scenarios}
\begin{figure*}[ht]
\centering
\subfigure[5 remote GPUs over 1GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws3.png}
\label{subfig:aws1}}
\quad
\subfigure[8 remote GPUs over 10GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws2.png}
\label{subfig:aws2}}
\subfigure[13 remote GPUs over 1GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws1.png}
\label{subfig:aws3}}
\caption{Different scenario configurations where an AWS instance acting as a client is using several remote GPUs}
\label{fig:aws}
\end{figure*}

\subsection{Experiments}
\subsection{Results}
Flexibility and economical expenses

\section{GPGPU Shared Service in OpenStack}
In this section is explained all the work related to OpenStack that has been done, from the development of an external module to handle remote GPUs to the physical setup and its testing.
\subsection{Managing remote GPUs with OpenStack}
The main idea of this solution is to reach the scenario that could be seen in Figure~\ref{fig:external}, where a new shared service takes part in to the OpenStack Architecture.
This new service is in charge of GPGPU computation, bringing more flexibility when it comes to GPUs.
As it is shown in Figure~\ref{fig:internal}, we have altered the OpenStack original Dashboard with a new parser, 
which split the HTTP query in order to make use of both, the GPGPU API for everything related to GPUs, and the nova API for the rest of the computation. 
The new GPGPU Service has brought a new feature which brings more flexibility when managing GPUs, from now on, we can create ``GPU-pools''. 
A ``GPU-pool'' is a set of independent GPUs (logically disattached from the nodes) that can be assigned to one or more instances.

>>>>

\subsection{Testbed Scenarios}
\begin{figure*}[!t]
\centering
\subfigure[5 remote GPUs over 1GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws3.png}
\label{subfig:aws1}}
\quad
\subfigure[8 remote GPUs over 10GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws2.png}
\label{subfig:aws2}}
\subfigure[13 remote GPUs over 1GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws1.png}
\label{subfig:aws3}}
\caption{Different configurations where an AWS instance acting as a client is using several remote GPUs}
\label{fig:aws}
\end{figure*}

\subsection{Experiments}
\subsection{Results}

\begin{figure}[!t]
  \centering
  \includegraphics[width=\linewidth]{images/aws-mont2.png}
  \caption{Montecarlo execution time}
  \label{fig:internal}
\end{figure}
\begin{figure}[!t]
  \centering
  \includegraphics[width=\linewidth]{images/aws-mont1.png}
  \caption{Montecarlo options per second}
  \label{fig:internal}
\end{figure}

Flexibility and economical expenses

\section{GPGPU Shared Service in OpenStack}
In this section all the work related to OpenStack that has been done is explained, from the development of an external module to handle remote GPUs to the physical setup and its testing.
\subsection{Managing remote GPUs with OpenStack}
The main idea of this solution is to reach the scenario that could be seen in Figure~\ref{fig:external}, where a new shared service takes part in to the OpenStack Architecture.
This new service is in charge of GPGPU computation, bringing more flexibility when it comes to GPUs.
As it is shown in Figure~\ref{fig:internal}, we have altered the OpenStack original Dashboard with a new parser, 
which split the HTTP query in order to make use of both, the GPGPU API for everything related to GPUs, and the nova API for the rest of the computation. 
The new GPGPU Service has brought a new feature which brings more flexibility when managing GPUs, from now on, we can create ``GPU-pools''. 
A ``GPU-pool'' is a set of independent GPUs (logically disattached from the nodes) that can be assigned to one or more instances.
